Continuous Generalization of Buildings

### 2017-03-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added some references for our introduction

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{todonotes}
\usepackage[backend=bibtex,bibstyle=authoryear,citestyle=authoryear,
firstinits=true,doi=false,isbn=false,url=false,eprint=false,dashed=false,natbib=true]{biblatex}
%\renewcommand*{\bibfont}{\small}
\addbibresource{References.bib}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

@@

@@

The first way is that we cover the smallest block at each step. 
Should we consider the density of the buildings? 
\marginalcomment{relevant comment. If small buildings exist in 
	all blocks, there will be small buildings remaining at small 
	scales in the blocks that have not been covered.}
A disadvantage 
is that some small buildings in a large block may exist very 
long.
Alternatively, we may cover two buildings together if they are 
close enough, say the distance is smaller than d. We can 
increase d so that we will cover more and more buildings 
together. To avoid overlap between two covers, we may need to 
use Voronoi diagrams of the original buildings. We can cover 
buildings without overlap if we always use a cover inside the 
Voronoi cells of these buildings. This idea about Voronoi cells 
is used in Topologically Safe Curved Schematization (van Goethem 
et al. 2013). We may need to try different possible covers. 
Unfortunately, this trying may be very time-consuming, probably 
NP-hard.

@@

We have two requirements for an output map.
The first one is that the distance between two 
buildings should be at least $d_i=0.2 \mathrm{mm}/S_i$, where 
$S_i$ is the scale of map $i$.
The second requirement is that a building with area less than 
$A_i=0.16\mathrm{mm}^2/S^2_i$ should be eliminated. Roughly, a 
building with width less than 
$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S$ should be eliminated.
In order to make sure that some small buildings will be 
eliminated, the radius $r_i$ that we use to buffer buildings 
should be smaller than $\frac{1}{2}w_i$. We simply use 
$r_i=\frac{1}{4}w_i$.
Our buildings may have been buffered with radius, in total, 
$r_{i-1}$ from previous steps.
Therefore, we only need to buffer with radius $r_i-r_{i-1}$ at 
the new 
step.

Our generalisation is as following $4$ steps:
\begin{enumerate}[label=(\alph*),leftmargin=2\parindent]
	\item We buffer buildings with 
	radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
	overlapping each other.
	\item Then we buffer the results with $-\frac{1}{2}d_i$.
	\item In order to 
	remove some spikes from the buffering, we buffer the new 
	results with $-\epsilon_i$.
	\item To compensate, we buffer with $\epsilon_i$.	
\end{enumerate}
We simply set 
$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
operations, we eliminate the buildings with area less than 
$d^2_i$.

>>>>

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

\usepackage[backend=bibtex,
bibstyle=authoryear, %without indices before names; year after 
%names
%style=authoryear,
citestyle=authoryear,
maxbibnames=20,maxcitenames=2,
firstinits=true,
%terseinits=true, %remove periods after initials of first names
%style=apa, %
%sorting=ydnt, %Sort bibliography by year (descending), name, 
%title
doi=false,isbn=false,url=false,
eprint=false,dashed=false]{biblatex}

%\renewcommand*{\bibfont}{\small} %set the font size of the 
%references
%\renewcommand*{\nameyeardelim}{\addspace} %\remove the comma 
%between author and year citations
%\renewcommand*{\revsdnamepunct}{} %remove commas between last 
%%and first names in bibliography
%\renewcommand{\labelnamepunct}{\addspace} %remove the 
%%punctuation after the year in bibliography
%\renewcommand{\finentrypunct}{} %remove the full stop at the 
%%end of each bibliography entry
\renewcommand*{\revsdnamepunct}{} %remove commas between last 
%and first names in bibliography

%remove "In:" for articles in bibliography
\renewbibmacro{in:}{\ifentrytype{article}{}
	{\printtext{\bibstring{in}\intitlepunct}}}

\addbibresource{References.bib}

@@

\section{Introduction}
\label{sec:Introduction}

The papers we may review:   
\textcite{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},

Rules for building simplification; see \textcite{Lee2005}

@@

The first way is that we cover the smallest block at each step. 
Should we consider the density of the buildings? 
\marginalcomment{relevant comment. If small buildings exist in 
	all blocks, there will be small buildings remaining at small 
	scales in the blocks that have not been covered.}
A disadvantage 
is that some small buildings in a large block may exist very 
long.
Alternatively, we may cover two buildings together if they are 
close enough, say the distance is smaller than d. We can 
increase d so that we will cover more and more buildings 
together. To avoid overlap between two covers, we may need to 
use Voronoi diagrams of the original buildings. We can cover 
buildings without overlap if we always use a cover inside the 
Voronoi cells of these buildings. This idea about Voronoi cells 
is used in \textcite{vanGoethem2013}. We may need to try 
different 
possible covers. 
Unfortunately, this trying may be very time-consuming, probably 
NP-hard.

@@

We have two requirements for an output map.
The first one is that the distance between two 
buildings should be at least $d_i=0.2 \mathrm{mm}/S_i$, where 
$S_i$ is the scale of map $i$.
The second requirement is that a building with area less than 
$A_i=0.16\mathrm{mm}^2/S^2_i$ should be eliminated. Roughly, a 
building with width less than 
$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S_i$ should be eliminated.
In order to make sure that some small buildings will be 
eliminated, the radius $r_i$ that we use to buffer buildings 
should be smaller than $\frac{1}{2}w_i$. We simply use 
$r_i=\frac{1}{4}w_i$.
Our buildings may have been buffered with radius, in total, 
$r_{i-1}$ from previous steps.
Therefore, we only need to buffer with radius $r_i-r_{i-1}$ at 
the new 
step.

Our generalisation is as following $4$ steps:
\begin{enumerate}[label=(\alph*),leftmargin=2\parindent]
	\item We buffer buildings with 
	radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
	overlapping each other.
	\item Then we buffer the results with $-\frac{1}{2}d_i$.
	\item In order to 
	remove some spikes from the buffering, we buffer the new 
	results with $-\epsilon_i$.
	\item To compensate, we buffer with $\epsilon_i$.	
\end{enumerate}
We simply set 
$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
operations, we eliminate the buildings with area less than 
$A_i$.
